---
title : "17125760041_Assignment_3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

DSC402 ASSIGNMENT 3 HACKATHON - PHASE I PROBLEM: DEVELOP A CLASSIFICATION MODEL THAT WILL IDENTIFY THE COMPENSATION LEVEL OF AN INDIVIDUAL. STEPS

Develop the classification models Decision Tree / kNN / Naïve Bayes

1. Attached is a 'sample data' and below are the features of the data. Review the sample data (Model_Data_sample.csv) and the description below. Build an understanding of the data and plan your approach to build a model

2. Define your data exploration, imputation and visualization approach. (1 Mark)

3. You will be sent the complete data file for modeling. (Model_Data.csv)

4. Set seed for sampling (your roll number) Eg. Set.seed(17125760345)

5. Split model data into train (80%) and test (20%)

6. Build 3 Models, each using one of different type of algorithm. Send me the model building command. (1 mark each + 1 for creative "DS" think = total 4 marks)
model1 = 
model2 =
model3 =

7. Predict your model performance on each of the 3 models and submit ( 1 mark each = total 3 marks)
model1_accuracy= 79.9
model2_accuracy = 83.3
modell3_accuracy= 79.23

8. Generalization ( 1 mark)

9. Upload details into your account on GIT Hub ( 1 mark)


#---NAVIEs BAYES--------

```{r}
hackton <- read.csv(file = "D:/Data Science 2017/Manipal Academy of Data Science/MGADS TERM2/1 Machine Learning/Hackton/Model_Data.csv")
hackton
```
```{r}
library(class)
library(tree)
library(e1071)
library(VIM)
library(missForest)
library(datasets)
library(data.table)
```

```{r}
set.seed(41)
sample1 <- sample.int(n=nrow(hackton),size = floor(.8*nrow(hackton)),replace = F)
sample1
```


```{r}
hck_train <- hackton[sample1,]
hck_test <- hackton[-sample1,]
hck_train
hck_test
hck_train$salary = as.factor(hck_train$salary)
```

```{r}
hck_model_n<- naiveBayes(salary ~ age + workclass+ education+ maritalstatus+ occupation+ relationship + race + sex+ hourperweek+ nativecountry, data = hck_train)
hck_model_n
```

```{r}
hck_model_n<- predict(hck_model_n,hck_test[,-1])
hck_model_n
```

```{r}
confmat_hck <- table(hck_model_n,hck_test$salary)
confmat_hck
```

```{r}
accuracy_n = sum(diag(confmat_hck))/sum(confmat_hck)
accuracy_n
```

#-----DECISION TREE---------

```{r}
hackton <- read.csv(file = "D:/Data Science 2017/Manipal Academy of Data Science/MGADS TERM2/1 Machine Learning/Hackton/Model_Data.csv")
hackton
```

```{r}
set.seed(41)
sample1 <- sample.int(n=nrow(hackton),size = floor(.8*nrow(hackton)),replace = F)
sample1
```

```{r}
hck_train <- hackton[sample1,]
hck_test <- hackton[-sample1,]
hck_train
hck_test
```

```{r}
hck_model_d<- tree(salary ~ age + workclass+ education+ maritalstatus+ occupation + race + sex + hourperweek, data = hck_train)
hck_model_d
hck_pred <- predict(hck_model_d,hck_test)
hck_pred
```
```{r}
maxid99 <- function(arr){
  return(which(arr==max(arr)))
}
maxid99
```

```{r}
idx99 <- apply(hck_pred,c(1),maxid99)
idx99
```
```{r}
hck_model_pr <- c(0,1)[idx99]
hck_model_pr
```

```{r}
hck_comf <- table(hck_model_pr,hck_test$salary)
hck_comf
hck_acc_d <- sum(diag(hck_comf))/sum(hck_comf)
hck_acc_d
```


#-----KNN-----=
```{r}
hackton <- read.csv(file = "D:/Data Science 2017/Manipal Academy of Data Science/MGADS TERM2/1 Machine Learning/Hackton/Model_Data.csv")
hackton
```

```{r}
for(i in 1:ncol(hackton)){
  hackton[,i]=as.numeric(hackton[,i])
}
```

```{r}
set.seed(41)
sample1 <- sample.int(n=nrow(hackton),size = floor(.8*nrow(hackton)),replace = F)
sample1
```

```{r}
hck_train <- hackton[sample1,]
hck_test <- hackton[-sample1,]
hck_train
hck_test
hck_train_data <- hck_train[,c(1:14)]
hck_test_data <- hck_test[,c(1:14)]

hck_train_label <- hck_train[,15]

hck_test_label <- hck_test[,15]

hck_train_label
hck_test_label
hck_train$salary = as.factor(hck_train$salary)
```
```{r}
k=9
```

```{r}
hck_pre_label <- knn(train = hck_train,test = hck_test, cl = hck_train_label,k)
hck_pre_label
```

```{r}

confmat_k = table(hck_test_label,hck_pre_label)
confmat_k
```

```{r}

accuracy_k <- sum(diag(confmat_k))/sum(confmat_k)
accuracy_k
```



